\chapter*{Glossary}
\addcontentsline{toc}{chapter}{Glossary}

\setlength{\parindent}{0pt}
\hspace{1cm}{This glossary provides definitions for key terms, acronyms, and technical concepts used throughout this document.}

\begin{description}
  \item[AArch64] 64-bit ARM architecture (ARM64), used in the Raspberry Pi 4's Cortex-A72 processor.
  \item[Acknowledge] User action to mark an ML recommendation as reviewed, updating the \texttt{user\_acknowledged} field in the database.
  \item[ADC (Analog-to-Digital Converter)] Hardware component (ADS1115) that converts analog sensor signals to digital values readable by the Raspberry Pi.
  \item[ADS1115] 16-bit precision I2C-compatible ADC module used for reading analog sensors (pH, TDS).
  \item[ADS7846] Resistive touchscreen controller chip used in the Waveshare 3.5" display.
  \item[Alert] System-generated notification when sensor readings exceed predefined thresholds.
  \item[Alert Threshold] Configurable confidence level (default 70\%) above which ML predictions trigger system alerts.
  \item[BCM2711] Broadcom System-on-Chip (SoC) powering the Raspberry Pi 4 Model B.
  \item[Buildroot] Open-source tool for generating custom embedded Linux systems, used to create the LeafSense OS image (version 2025.08).
  \item[BusyBox] Lightweight Unix utilities collection used for system initialization in embedded Linux.
  \item[CMake] Cross-platform build system generator used for compiling the LeafSense C++ application.
  \item[Condition Variable] POSIX synchronization primitive used for thread signaling and coordination.
  \item[Cortex-A72] ARM processor core architecture in the Raspberry Pi 4, running at 1.8GHz.
  \item[COTS (Commercial Off-The-Shelf)] Pre-built hardware or software components used in the project.
  \item[Cross-Compilation] Compiling code on one architecture (x86) for execution on another (ARM64).
  \item[Daemon] Background process running continuously without user interaction (e.g., database daemon).
  \item[DS18B20] Digital waterproof temperature sensor using the 1-Wire protocol.
  \item[DS3231] High-precision Real-Time Clock (RTC) module with I2C interface.
  \item[DTO (Data Transfer Object)] Structured data container for passing information between system layers.
  \item[EC (Electrical Conductivity)] Measurement of nutrient concentration in hydroponic solution, expressed in $\mu$S/cm.
  \item[Entropy (Shannon)] Information theory metric measuring uncertainty in probability distribution; used for OOD detection. Formula: $H = -\sum p_i \log_2(p_i)$.
  \item[ERD (Entity-Relationship Diagram)] Visual representation of database structure and table relationships.
  \item[eudev] Device manager for Linux systems, handles dynamic device creation.
  \item[Framebuffer] Memory buffer containing pixel data for display output (e.g., /dev/fb1).
  \item[FIFO (First In, First Out)] Queue data structure used in message passing.
  \item[glibc] GNU C Library, standard C library required for ONNX Runtime compatibility.
  \item[GPIO (General Purpose Input/Output)] Configurable digital pins on the Raspberry Pi for hardware control.
  \item[Green Ratio] Percentage of green/plant-like pixels in an image, used for OOD detection. Images with less than 5\% green are rejected as non-plant.
  \item[GUI (Graphical User Interface)] Qt5/Qt6-based touchscreen interface for user interaction.
  \item[HAL (Hardware Abstraction Layer)] Software layer isolating application logic from hardware-specific code.
  \item[HSV (Hue-Saturation-Value)] Color space used for plant color detection; green hue range is 35-85.
  \item[Hydroponics] Soil-free cultivation method using nutrient-rich water solutions.
  \item[Hysteresis] Control technique using upper and lower thresholds to prevent actuator oscillation.
  \item[I2C (Inter-Integrated Circuit)] Two-wire serial communication protocol for sensors and peripherals.
  \item[ILI9486] LCD display controller chip used in the Waveshare 3.5" touchscreen.
  \item[IPC (Inter-Process Communication)] Mechanisms for data exchange between separate processes.
  \item[ITC (Inter-Thread Communication)] Mechanisms for data exchange between threads within a process.
  \item[Kernel Module] Loadable code extending Linux kernel functionality (e.g., LED driver).
  \item[Kiosk Mode] GUI configuration running fullscreen without window manager overhead.
  \item[LeafSense] Real-Time Hydroponic Plant Monitoring System developed in this project.
  \item[libgpiod] Modern Linux library for GPIO control, replacing legacy sysfs interface.
  \item[linuxfb] Linux framebuffer Qt platform plugin for direct display rendering.
  \item[Message Queue] POSIX IPC mechanism for asynchronous data exchange between processes.
  \item[Middleware] Software layer between hardware drivers and application logic.
  \item[ML (Machine Learning)] AI techniques for automated plant disease and deficiency detection.
  \item[MobileNetV3-Small] Lightweight convolutional neural network architecture optimized for mobile/embedded devices; used in LeafSense for plant classification.
  \item[Multi-class Classification] ML task predicting one of several discrete categories (e.g., healthy, disease, deficiency, pest).
  \item[Mutex] Mutual exclusion lock for thread synchronization and resource protection.
  \item[NAT (Network Address Translation)] Network technique used for Raspberry Pi provisioning.
  \item[NEON] ARM SIMD (Single Instruction, Multiple Data) extensions for image processing acceleration.
  \item[ONNX (Open Neural Network Exchange)] Open format for ML model interoperability.
  \item[ONNX Runtime] High-performance inference engine for executing ONNX models in C++.
  \item[OOD (Out-of-Distribution)] Detection technique identifying inputs that differ significantly from training data; prevents false predictions on non-plant images.
  \item[OpenCV] Open Source Computer Vision library for image capture and processing.
  \item[OV5647] 5-megapixel camera sensor module for Raspberry Pi.
  \item[OOP (Object-Oriented Programming)] Software design paradigm used throughout LeafSense.
  \item[Peristaltic Pump] Precision fluid dosing pump for pH and nutrient adjustment.
  \item[pH] Measure of acidity/alkalinity (0--14 scale), critical for plant health.
  \item[PH-4502C] Analog pH sensor module used for water chemistry monitoring.
  \item[POSIX] Portable Operating System Interface standard for Unix-like systems.
  \item[pthreads] POSIX Threads library for multi-threaded programming in C/C++.
  \item[Qt] Cross-platform application framework for GUI development (Qt5/Qt6).
  \item[Qt Creator] Integrated development environment for Qt applications.
  \item[Raspberry Pi] Single-board computer (Model 4B) serving as the LeafSense processing unit.
  \item[Recommendation] Context-aware treatment suggestion generated by the ML pipeline, correlating predictions with current sensor readings.
  \item[Recommendation Panel] Side-by-side GUI component in the Gallery tab displaying ML recommendations alongside captured images.
  \item[RTC (Real-Time Clock)] Hardware module (DS3231) maintaining accurate time during power loss.
  \item[SCP (Secure Copy Protocol)] SSH-based file transfer protocol for deployment.
  \item[Softmax] Activation function converting raw model outputs (logits) into probability distribution summing to 1.0.
  \item[SoC (System-on-Chip)] Integrated circuit combining CPU, GPU, and peripherals (BCM2711).
  \item[SPI (Serial Peripheral Interface)] High-speed serial communication protocol for displays.
  \item[SQLite3] Lightweight, serverless SQL database engine for persistent storage.
  \item[SSH (Secure Shell)] Encrypted protocol for remote system access.
  \item[TDS (Total Dissolved Solids)] Measurement of nutrient concentration in ppm (parts per million).
  \item[Theme] Visual appearance mode (Light/Dark) for the GUI, configurable via Settings.
  \item[Thread] Lightweight execution unit within a process, managed by pthreads.
  \item[Toolchain] Collection of compilers and tools for cross-compilation (GCC 14.3.0).
  \item[UML (Unified Modeling Language)] Standard notation for software design diagrams.
  \item[USB-C] Power connector type for Raspberry Pi 4 (5V, 3A minimum).
  \item[V4L2 (Video4Linux2)] Linux kernel API for video capture devices.
  \item[Waveshare] Manufacturer of the 3.5" ILI9486 touchscreen display used in LeafSense.
  \item[1-Wire] Single-wire communication protocol used by DS18B20 temperature sensor.
\end{description}